PRIMUS: Effects of Galaxy Environment on the Quiescent Fraction Evolution at \lowercase{\textit{z}}$<0.8$

### 2015-03-20 qfenv_paper/qf_environment.tex
more changes to address ref report

%define general packages
\usepackage{epsfig}
\usepackage{rotating}
\usepackage{amsmath}
\usepackage{natbib}
\usepackage{footnote}
\usepackage{courier}

%internal short cuts
\def \HgA {H$\gamma_A$}
\def \Hbp {H$\beta ^\prime$}
\def \lowenvthresh {0.5}
\def \highenvthresh {3.0}
\def \apradius{2.5}
\def \apheight{35}

@@

\title{PRIMUS: Effect of Galaxy Environment on the Quiescent Fraction Evolution at $z < 0.8$}

@@

them. However, in the recent Universe a substantial fraction of the

@@

\keywords{cosmology:observations --- galaxies: evolution --- galaxies:groups --- galaxies: star formation}

@@

\begin{figure*}
    \begin{center}
        \leavevmode
        \epsscale{1.2}
	\plotone{fig_edp_sdss_z0_05_0_12_primus_z0_2_1_0_Mr_redshift.png}
        \caption{Absolute magnitude $M_{r}$ versus redshift for our mass complete galaxy sample (black squares) with the Environment Defining Population (red circles) plotted on top. Both samples are divided into redshift bins: $z = 0.05-0.12$, $0.2-0.4$, $0.4-0.6$, and $0.6-0.8$ (panels left to right). The lowest redshift bin ($z \approx 0.05-0.12$; leftmost panel) contain our galaxy sample and EDP selected from SDSS. The rest contain galaxies and EDP selected from PRIMUS. The redshift limits for the lowest redshift bin are empirically selected based on the bright and faint limits of SDSS galaxies. Stellar mass completeness limits, described in Section \ref{sec:target}, are imposed on the galaxy population. Meanwhile, $M_{r}$ limits are applied to the EDP such that the number density in each panel are equivalent (Section \ref{sec:environment}).} \label{fig:targetEDP}
    \end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PRIMUS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{PRIMUS} \label{sec:primus}
At intermediate redshifts we use multiwavelength imaging and
spectroscopic redshifts from PRIMUS, a faint galaxy survey with $\sim
120,000$ redshifts ($\sigma_z/(1+z) \approx 0.5 \%$) within the range
$z \approx 0-1.2$. The survey was conducted using the IMACS
spectrograph on the Magellan I Baade $6.5$-m telescope with a slitmask and low dispersion prism. For details on the PRIMUS observation methods such as survey design, targeting, and data summary, we refer readers to the survey papers (\citealt{Coil:2011aa, Cool:2013aa}).

While the PRIMUS survey targeted seven distinct extragalactic deep fields for a total of $\sim 9 \; \mathrm{deg}^2$, we restrict our sample to five fields that have $GALEX$ and {\em Spitzer}/IRAC imaging for a total of $\sim 5.5 \; \mathrm{deg}^2$ (similar to the sample selection in \citealt{Moustakas:2013aa}). Four of these fields are a part of the {\em Spitzer} Wide-area Infrared Extragalactic Survey (SWIRE\footnote{http://swire.ipac.caltech.edu/swire/swire.html}): the European Large Area ISO Survey - South $1$ field (ELAIS-S1\footnote{http://dipastro.pd.astro.it/esis}), the Chandra Deep Field South SWIRE field (CDFS), and the XMM Large Scale Structure Survey field (XMM-LSS). The XMM-LSS consists of two separate but spatially adjacent fields: the Subaru/XMM-Newton DEEP Survey field (XMM-SXDSS\footnote{http://www.naoj.org/cience/SubaruProject/SDS}) and the Canadian-France-Hawaii Telescope Legacy Survey field (XMM-CFHTLS\footnote{http://www.cfht.hawaii.edu/Science/CFHLS}). Our fifth and final field is the Cosmic Evolution Survey (COSMOS\footnote{http://cosmos.astro.caltech.edu}) field. For all of our fields we have near-UV (NUV) and far-UV (FUV) photometry from the {\em GALEX} Deep Imaging Survey (DIS; \citealt{Martin:2005aa, Morrissey:2005aa}) as well as ground-based optical and {\em Spitzer}/IRAC mid-infrared photometric catalogs. \cite{Moustakas:2013aa} provides detailed descriptions of integrated flux calculations in the photometric bands for each of our fields. Furthermore, we derive the {\em K-corrections} from the photometry using \texttt{K-correct} (v4.2; \citealt{Blanton:2007aa}).

Finally, using the spectroscopic redshift and broad wavelength photometry we apply \texttt{iSEDfit}, a Bayesian SED modeling code, to calculate stellar masses and star formation rates (SFRs) for our sample galaxies (\citealt{Moustakas:2013aa}). \texttt{iSEDfit} uses the redshift and the observed photometry of the galaxies to determine the statistical likelihood of a large ensemble of generated model SEDs. The model SEDs are generated using Flexible Stellar Population Synthesis (FSPS) models (\citealt{Conroy:2010aa}) based on the \cite{Chabrier:2003aa} IMF, along with other prior parameters discussed in Section 4.1 and Appendix A of \cite{Moustakas:2013aa}. For the observed photometry, we use the {\em GALEX} FUV and NUV, the two shortest IRAC bands at $3.6$ and $4.5 \mu \mathrm{m}$ (the two longer-wavelength IRAC channels are excluded because \texttt{iSEDfit} does not model hot dust or polycyclic aromatic hydrocarbons emission lines), and the optical bands.

@@

We now have a stellar mass complete sample derived from SDSS-{\em
  GALEX} and PRIMUS data. Since our sample is derived from two
different surveys, we account for the disparity in the redshift
uncertainty. While PRIMUS provides a large number of redshifts out to
$z = 1$, due to its use of a low dispersion prism, the redshift
uncertainties are significantly larger ($\sigma_{z}/(1+z) \approx 0.5
\%$) than the uncertainties of the SDSS-{\em GALEX} redshifts. In order to have
comparable environment measures throughout our redshift range, we
apply PRIMUS redshift uncertainties to our galaxy sample selected from
SDSS-{\em GALEX}. For each SDSS-{\em GALEX} galaxy, we adjust its
redshift by randomly sampling a Gaussian distribution with standard
deviation $\sigma = 0.005 (1+z_{\mathrm{SDSS}-GALEX})$, where
$z_{\mathrm{SDSS}-GALEX}$ is the redshift of the galaxy.

@@

    \epsfig{file=fig_envcount_cylr2_5h35_thresh75_sdss_z0_05_0_12_primus_z0_2_1_0_lowenv0_5_highenv3_0_primuszerr_masslimit_edgecut_histogram.png, width=0.45\textwidth}
    \caption{Normalized distribution of environment measurements ($n_{\mathrm{env}}$) for our mass complete galaxy sample within the survey edges. A fixed cylindrical aperture of $R_{\mathrm{ap}} =\apradius\;\mathrm{Mpc}$ and $H_{\mathrm{ap}} = \apheight\; \mathrm{Mpc}$ is used to measure environment. The star-forming galaxies contribution to the distribution is colored in blue and diagonally patterned. The contribution from quiescent galaxies is colored in red. Galaxies with $n_{\mathrm{env}} < 0.5$ are in low density environments and galaxies with $n_{\mathrm{env}} > 3.0$ are in high density environment. We note that the significant difference among the SDSS distribution and the PRIMUS distributions above is due to the different stellar mass completeness limits imposed on each redshift bin of our galaxy sample.}      \label{fig:envcount}

@@

For our aperture, we use a cylinder of dimensions: $R_{\mathrm{ap}} =
\apradius\;
\mathrm{Mpc}$ and $H_{\mathrm{ap}} = \apheight\; \mathrm{Mpc}$.  We use a
cylindrical aperture to account for the PRIMUS redshift
errors and redshift space distortions (i.e. ``Finger of God"
effect). As \cite{Cooper:2005aa} and \cite{Gallazzi:2009aa} find, 
$\pm 1000 \; \mathrm{km} \;\mathrm{s^{-1}}$ optimally reduces the effects of redshift space
distortions. The PRIMUS redshift uncertainty at $z \sim 0.7$
corresponds to $\sigma_z < 0.01$, so our choice of $\apheight\;
\mathrm{Mpc}$ for the aperture height accounts for both of these effects. Our choice of
cylinder radius was motivated by scale dependence analyses in the
literature (\citealt{Blanton:2006aa, Wilman:2010aa, Muldrew:2012aa}),
which suggest that galactic properties such as color and quiescent
fractions are most strongly dependent on scales $< 2$ Mpc, around the
host dark matter halo sizes.

@@

In Figure \ref{fig:envcount} we present the distribution of environment measurements ($n_{\mathrm{env}}$) for our final galaxy sample in redshift bins: $z = 0.05 - 0.12$, $0.2 - 0.4$, $0.4-0.6$, and $0.6-0.8$. The quiescent galaxy contributions are colored in red while the star-forming galaxy contributions are colored in blue and patterned. We classify galaxies with $n_{\mathrm{env}} < 0.5$ to be in low density environments and galaxies with $n_{\mathrm{env}} > 3.0$ to be in high density environments.

Although we imposed PRIMUS redshift errors on our SDSS galaxies to consistently measure environment throughout our entire sample, we note a significant discrepancy between the $n_{\mathrm{env}}$ distributions of the SDSS and PRIMUS samples. For example, in each of the PRIMUS redshift bins, $\sim 40 \%$ of galaxies in the redshift bin are in low density environments and roughly $30 \%$ are in high density environments. In contrast, in the SDSS redshift bin, $\sim 20 \%$ of galaxies in the redshift bin are in low density environments and $\sim 35 \%$ are in high density environments. We remind the reader that this is mainly due to the varying stellar mass-completeness limits imposed on our galaxy sample for each redshift bins and does not affect our results. 
\begin{figure*}
  \begin{center}
    \leavevmode
    \epsfig{file=fig_smf_cylr2_50000h35_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_2envbin_lowenv0_5_highenv3_0_lit_primuszerr.eps, height=0.75\textwidth,angle=90}
     \caption{Evolution of stellar mass functions of star-forming (top) and quiescent (bottom) galaxies in 
low (left) and high (right) density environments throughout the redshift range
$z=0$--$0.8$. The environment of each galaxy  
was calculated using a cylindrical aperture size of $R=\apradius \: \mathrm{Mpc}$ and $H=\apheight \: \mathrm{Mpc}$ and  
classified as low environment when $n_{\mathrm{env}} < 0.5$ and as high environment when $n_{\mathrm{env}} > 3.0$. The SMFs use mass bins of 
width $\Delta \mathrm{log}(\mathcal{M}/\mathcal{M}_{\odot})=0.2$. In each panel we use shades of blue 
(star-forming) and orange (quiescent) to represent the SMF at different redshift, higher redshifts being
progressively lighter.}      \label{fig:smf}
    \end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% STELLAR MASS FUNCTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results: Stellar Mass Function} \label{sec:smf}
Our galaxy sample has so far been classified into quiescent or
star-forming and low or high density environments. We further divide
these subsamples into redshift bins: $0.05-0.12$, $0.2-0.4$,
$0.4-0.6$, and $0.6-0.8$ for a total of 16 subsamples. In Section \ref{sec:smfcalc}, we calculate the SMF for each of these subsamples. Then we examine the evolution of active and quiescent subsample SMFs in different environments in Section \ref{sec:smfevol}.  
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% STELLAR MASS FUNCTION CALCULATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Stellar Mass Function Calculations} \label{sec:smfcalc} 
To calculate the SMFs we employ a non-parametric $1/{V_{\mathrm{max}}}$ estimator commonly used for galaxy luminosity functions and stellar mass functions in order to account for Malmquist bias, as done in \cite{Moustakas:2013aa} and discussed in the review \cite{Johnston:2011aa}. The differential SMF is given by the following equation:
\begin{equation} \label{eq:phi}
\Phi(\mathrm{log}\: \mathcal{M}) \Delta(\mathrm{log} \:\mathcal{M}) = \sum\limits_{i=1}^{N} \frac{w_i}{V_{\mathrm{max,avail},i}}. 
\end{equation}
$w_i$ is the statistical weight of galaxy $i$ and $\Phi(\mathrm{log}\:
\mathcal{M}) \Delta(\mathrm{log}\: \mathcal{M})$ is the number of galaxies
($N$) per unit volume within the stellar mass range $[\mathrm{log}
  \mathcal{M},\: \mathrm{log} \mathcal{M}+\Delta(\mathrm{log}\mathcal{M})]$. The equation above is the same as Equation 3 in \cite{Moustakas:2013aa} except that we use $V_{\mathrm{max,avail}}$ instead than $V_{\mathrm{max}}$, to account for the edge effects of the survey discussed in Section \ref{sec:edgeeffect}.

@@

\begin{figure*}
    \begin{center}
        \leavevmode
        \epsfig{file=fig_qf_cylr2_50000h35_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lowenv0_5_highenv3_0_lit_primuszerr.eps, height=0.75\textwidth,angle=90}
        \caption{Evolution of the quiescent fraction $f_{\mathrm{Q}}$ for
          galaxies in low (left) and high (right) density
          environments for $z < 0.8$. $f_{\mathrm{Q}}$s were calculated
          using the SMFs in Figure \ref{fig:smf}, as described in Section \ref{sec:qfevol}. Darker shading indicates lower redshift and the width represents the standard jackknife uncertainty.}         \label{fig:qf}
    \end{center}
\end{figure*}

@@

For our PRIMUS sample at $z \sim 0.3$, over $10^{9.5} \mathcal{M}_{\odot} < \mathcal{M}_{*} < 10^{11} \mathcal{M}_{\odot}$ $f_{\mathrm{Q}}$ ranges from $\sim 0.2$ to $\sim 0.65$ for low density environment, while at high density environment $f_{\mathrm{Q}}$ ranges from $\sim 0.2$ to $\sim 0.8$. Similarly, at $z \sim 0.5$, over $10^{10} \mathcal{M}_{\odot} < \mathcal{M}_{*} < 10^{11.2} \mathcal{M}_{\odot}$ $f_{\mathrm{Q}}$ ranges from $\sim 0.3$ to $\sim 0.6$ for low density environment and $f_{\mathrm{Q}}$ ranges from $\sim 0.3$ to $\sim 0.7$. Finally in our highest redshift bin $z \sim 0.7$, over the mass range $10^{10.5} \mathcal{M}_{\odot} < \mathcal{M}_{*} < 10^{11.5} \mathcal{M}_{\odot}$, $f_{\mathrm{Q}}$ ranges from $\sim 0.35$ to $\sim 0.6$ for low density and $\sim 0.45$ to $\sim 0.8$ for high density. For the entire redshift range of our sample, $f_{\mathrm{Q}}$ in high density environment is higher than $f_{\mathrm{Q}}$ in low density environments.

@@

\begin{figure}
    \begin{center}
        \leavevmode
        \epsscale{1.0}
        \epsfig{file=fig_qffit_cylr2_50000h35_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lowenv0_5_highenv3_0_fidmasscomp11_0_10_5_lit_primuszerr.eps, height=0.45\textwidth}
        \caption{The evolution of the quiescent fraction at fiducial
          mass, $f_{Q}(\mathcal{M}_{\mathrm{fid}})$, for low (blue) and
          high (red) density environments within the redshift range $z
          = 0.0 - 0.8$. We present the $f_{Q}(\mathcal{M}_{\mathrm{fid}})$
          evolution for $\mathcal{M}_{\mathrm{fid}} = 10^{10.5}
          \mathcal{M}_\odot$ (solid fill) and $10^{11}
          \mathcal{M}_\odot$ (patterned fill) with the uncertainty of
          the best-fit parameter $b$ in Equation \ref{eq:qffit}
          represented by the width of the line. While the high density $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$ is greater than low density environment $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$ over the entire redshift range of our sample, there is a significant increase in $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$ over cosmic time for both environments. For the environment cut-offs ($n_{\mathrm{env}} < 0.5$ for low and $n_{\mathrm{env}} > 3.0$ for high), there is no significant difference in the slope of the evolution between the environments.}         \label{fig:qffit}
    \end{center}
\end{figure}

>>>>

%define general packages
\usepackage{epsfig}
\usepackage{rotating}
\usepackage{amsmath}
\usepackage{footnote}
\usepackage{courier}

%internal short cuts
\def \HgA {H$\gamma_A$}
\def \Hbp {H$\beta ^\prime$}
\def \lowenvthresh {0.0}
\def \highenvthresh {3.0}
\def \apradius{2.5}
\def \apheight{35}

@@

\title{PRIMUS: Effects of Galaxy Environment on the Quiescent Fraction Evolution at \lowercase{\textit{z}}$<0.8$}

@@

them. {\bf In other words}, in the recent Universe a substantial fraction of the

@@

\keywords{cosmology: observations --- galaxies: evolution --- galaxies: groups --- galaxies: star formation}

@@

\begin{figure*}
    \begin{center}
        \leavevmode
	\includegraphics[scale=0.475]{fig1.pdf}
        \caption{Absolute magnitude $M_{r}$ versus redshift for our mass complete galaxy sample (black squares) with the Environment Defining Population (red circles) plotted on top. Both samples are divided into redshift bins: $z = 0.05-0.12$, $0.2-0.4$, $0.4-0.6$, and $0.6-0.8$ (panels left to right). The lowest redshift bin ($z \approx 0.05-0.12$; leftmost panel) contain our galaxy sample and EDP selected from SDSS. The rest contain galaxies and EDP selected from PRIMUS. The redshift limits for the lowest redshift bin are empirically selected based on the bright and faint limits of SDSS galaxies. Stellar mass completeness limits, described in Section \ref{sec:target}, are imposed on the galaxy population. Meanwhile, $M_{r}$ limits are applied to the EDP such that the number density in each panel are equivalent (Section \ref{sec:environment}).} \label{fig:targetEDP}
    \end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PRIMUS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{PRIMUS} \label{sec:primus}
At intermediate redshifts we use multiwavelength imaging and
spectroscopic redshifts from PRIMUS, a faint galaxy survey with $\sim
120,000$ redshifts ($\sigma_z/(1+z) \approx 0.5 \%$) within the range
$z \approx 0-1.2$. The survey was conducted using the IMACS
spectrograph on the Magellan I Baade $6.5$-m telescope with a slitmask and low dispersion prism. For details on the PRIMUS observation methods such as survey design, targeting, and data summary, {\bf we refer readers to the \cite{Coil:2011aa}. For details on redshift fitting, redshift precision and survey completeness we refer readers to \cite{Cool:2013aa}.}

While the PRIMUS survey targeted seven distinct extragalactic deep fields for a total of $\sim 9 \; \mathrm{deg}^2$, we restrict our sample to five fields that have $GALEX$ and {\em Spitzer}/IRAC imaging for a total of $\sim 5.5 \; \mathrm{deg}^2$ (similar to the sample selection in \citealt{Moustakas:2013aa}). Four of these fields are a part of the {\em Spitzer} Wide-area Infrared Extragalactic Survey (SWIRE\footnote{http://swire.ipac.caltech.edu/swire/swire.html}): the European Large Area ISO Survey - South $1$ field (ELAIS-S1\footnote{http://dipastro.pd.astro.it/esis}), the Chandra Deep Field South SWIRE field (CDFS), and the XMM Large Scale Structure Survey field (XMM-LSS). The XMM-LSS consists of two separate but spatially adjacent fields: the Subaru/XMM-Newton DEEP Survey field (XMM-SXDS\footnote{http://www.naoj.org/cience/SubaruProject/SDS}) and the Canadian-France-Hawaii Telescope Legacy Survey field (XMM-CFHTLS\footnote{http://www.cfht.hawaii.edu/Science/CFHLS}). Our fifth and final field is the Cosmic Evolution Survey (COSMOS\footnote{http://cosmos.astro.caltech.edu}) field. For all of our fields we have near-UV (NUV) and far-UV (FUV) photometry from the {\em GALEX} Deep Imaging Survey (DIS; \citealt{Martin:2005aa, Morrissey:2005aa}) as well as ground-based optical and {\em Spitzer}/IRAC mid-infrared photometric catalogs. \cite{Moustakas:2013aa} provides detailed descriptions of integrated flux calculations in the photometric bands for each of our fields. Furthermore, we derive the {\em K-corrections} from the photometry using \texttt{K-correct} (v4.2; \citealt{Blanton:2007aa}).

Finally, using the spectroscopic redshift and broad wavelength photometry we apply \texttt{iSEDfit}, a Bayesian SED modeling code, to calculate stellar masses and star formation rates (SFRs) for our sample galaxies (\citealt{Moustakas:2013aa}). \texttt{iSEDfit} uses the redshift and the observed photometry of the galaxies to determine the statistical likelihood of a large ensemble of generated model SEDs. The model SEDs are generated using Flexible Stellar Population Synthesis (FSPS) models (\citealt{Conroy:2010aa}) based on the \cite{Chabrier:2003aa} IMF, along with {\bf a time dependent dust attenuation curve of \cite{Charlot:2000aa} and }other prior parameters discussed in Section 4.1 and Appendix A of \cite{Moustakas:2013aa}. For the observed photometry, we use the {\em GALEX} FUV and NUV, the two shortest IRAC bands at $3.6$ and $4.5 \mu \mathrm{m}$ (the two longer-wavelength IRAC channels are excluded because \texttt{iSEDfit} does not model hot dust or polycyclic aromatic hydrocarbons emission lines), and the optical bands.

@@

We now have a stellar mass complete sample derived from SDSS-{\em
  GALEX} and PRIMUS data. Since our sample is derived from two
different surveys, we account for the disparity in the redshift
uncertainty. While PRIMUS provides a large number of redshifts out to
$z = 1$, due to its use of a low dispersion prism, the redshift
uncertainties are significantly larger ($\sigma_{z}/(1+z) \approx 0.5
\%$) than the uncertainties of the SDSS redshifts. In order to have
comparable environment measures throughout our redshift range, we
apply PRIMUS redshift uncertainties to our galaxy sample selected from
SDSS-{\em GALEX}. {\bf For each SDSS-{\em GALEX} galaxy, we adjust its
redshift by randomly sampling a Gaussian distribution with standard
deviation $\sigma = 0.005 (1+z_\mathrm{SDSS})$, where
$z_\mathrm{SDSS}$ is the SDSS redshift of the galaxy.}

@@

    \includegraphics[scale=0.48]{fig2.pdf}
    \caption{Normalized distribution of environment measurements ($n_{\mathrm{env}}$) for our mass complete galaxy sample within the survey edges. A fixed cylindrical aperture of $R_{\mathrm{ap}} =\apradius\;\mathrm{Mpc}$ and $H_{\mathrm{ap}} = \apheight\; \mathrm{Mpc}$ is used to measure environment. The star-forming galaxies contribution to the distribution is colored in blue and diagonally patterned. The contribution from quiescent galaxies is colored in red. {\bf Galaxies with $n_{\mathrm{env}} = 0.0$ are in low density environments} and galaxies with $n_{\mathrm{env}} > 3.0$ are in high density environment. We note that the significant difference among the SDSS distribution and the PRIMUS distributions above is due to the different stellar mass completeness limits imposed on each redshift bin of our galaxy sample.}      \label{fig:envcount}

@@

For our aperture, we use a cylinder of dimensions: $R_{\mathrm{ap}} = \apradius\;
\mathrm{Mpc}$ and $H_{\mathrm{ap}} = \apheight\; \mathrm{Mpc}$. 
{\bf We note that $H_\mathrm{ap}$ is the full height of the cylinder and $R_\mathrm{ap}$ 
and $H_\mathrm{ap}$ are comoving distances.} We use a
cylindrical aperture to account for the PRIMUS redshift
errors and redshift space distortions (i.e. ``Finger of God"
effect). As \cite{Cooper:2005aa} and \cite{Gallazzi:2009aa} find, 
$\pm 1000 \; \mathrm{km} \;\mathrm{s^{-1}}$ optimally reduces the effects of redshift space
distortions. The PRIMUS redshift uncertainty at $z \sim 0.7$
corresponds to $\sigma_z < 0.01$, so our choice of $\apheight\;
\mathrm{Mpc}$ for the aperture height accounts for both of these effects. Our choice of
cylinder radius was motivated by scale dependence analyses in the
literature (\citealt{Blanton:2006aa, Wilman:2010aa, Muldrew:2012aa}),
which suggest that galactic properties such as color and quiescent
fractions are most strongly dependent on scales $< 2$ Mpc, around the
host dark matter halo sizes.

@@

In Figure \ref{fig:envcount} we present the distribution of environment measurements ($n_{\mathrm{env}}$) for our final galaxy sample in redshift bins: $z = 0.05 - 0.12$, $0.2 - 0.4$, $0.4-0.6$, and $0.6-0.8$. The quiescent galaxy contributions are colored in red while the star-forming galaxy contributions are colored in blue and patterned. We classify {\bf galaxies with $n_{\mathrm{env}} = 0.0$ to be in low density environments} and galaxies with $n_{\mathrm{env}} > 3.0$ to be in high density environments.

Although we imposed PRIMUS redshift errors on our SDSS galaxies to consistently measure environment throughout our entire sample, we note a significant discrepancy between the $n_{\mathrm{env}}$ distributions of the SDSS and PRIMUS samples. For example, in each of the PRIMUS redshift bins, $\sim 40 \%$ of galaxies in the redshift bin are in low density environments and roughly $30 \%$ are in high density environments. In contrast, in the SDSS redshift bin, $\sim 20 \%$ of galaxies in the redshift bin are in low density environments and $\sim 35 \%$ are in high density environments. We remind the reader that this is mainly due to the varying stellar mass-completeness limits imposed on our galaxy sample for each redshift bins and does not affect our results. 
\begin{figure*}
  \begin{center}
    \leavevmode
    \epsfig{file=fig3.pdf, height=0.75\textwidth}
     \caption{Evolution of stellar mass functions of star-forming (top) and quiescent (bottom) galaxies in 
low (left) and high (right) density environments throughout the redshift range
$z=0$--$0.8$. The environment of each galaxy  
was calculated using a cylindrical aperture size of $R=\apradius \: \mathrm{Mpc}$ and $H=\apheight \: \mathrm{Mpc}$ and  
{\bf classified as low environment when $n_{\mathrm{env}} = 0.0$ and }as high environment when $n_{\mathrm{env}} > 3.0$. The SMFs use mass bins of 
width $\Delta \mathrm{log}(\mathcal{M}/\mathcal{M}_{\odot})=0.2$. In each panel we use shades of blue 
(star-forming) and orange (quiescent) to represent the SMF at different redshift, higher redshifts being
progressively lighter.}      \label{fig:smf}
    \end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% STELLAR MASS FUNCTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results: Stellar Mass Function} \label{sec:smf}
Our galaxy sample has so far been classified into quiescent or
star-forming and low or high density environments. We further divide
these subsamples into redshift bins: $0.05-0.12$, $0.2-0.4$,
$0.4-0.6$, and $0.6-0.8$ for a total of 16 subsamples. In Section \ref{sec:smfcalc}, we calculate the SMF for each of these subsamples. Then we examine the evolution of active and quiescent subsample SMFs in different environments in Section \ref{sec:smfevol}.  
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% STELLAR MASS FUNCTION CALCULATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Stellar Mass Function Calculations} \label{sec:smfcalc} 
To calculate the SMFs we employ a non-parametric $1/{V_{\mathrm{max}}}$ estimator commonly used for galaxy luminosity functions and stellar mass functions in order to account for Malmquist bias, as done in \cite{Moustakas:2013aa} and discussed in the review \cite{Johnston:2011aa}. The differential SMF is given by the following equation:
\begin{equation} \label{eq:phi}
\Phi(\mathrm{log}\: \mathcal{M}) \Delta(\mathrm{log} \:\mathcal{M}) = \sum\limits_{i=1}^{N} \frac{w_i}{V_{\mathrm{max,avail},i}}. 
\end{equation}
$w_i$ is the statistical weight of galaxy $i$ and $\Phi(\mathrm{log}\:
\mathcal{M}) \Delta(\mathrm{log}\: \mathcal{M})$ is the number of galaxies
($N$) per unit volume within the stellar mass range $[\mathrm{log}
  \mathcal{M},\: \mathrm{log} \mathcal{M}+\Delta(\mathrm{log}\mathcal{M})]$. The equation above is the same as Equation 3 in \cite{Moustakas:2013aa} except that we use $V_{\mathrm{max,avail}}$ instead than $V_{\mathrm{max}}$, to account for the edge effects of the survey discussed in Section \ref{sec:edgeeffect}.

@@

\begin{figure*}
    \begin{center}
        \leavevmode
        \epsfig{file=fig4.pdf, height=0.75\textwidth,angle=90}
        \caption{Evolution of the quiescent fraction $f_{\mathrm{Q}}$ for
          galaxies in low (left) and high (right) density
          environments for $z < 0.8$. $f_{\mathrm{Q}}$s were calculated
          using the SMFs in Figure \ref{fig:smf}, as described in Section \ref{sec:qfevol}. Darker shading indicates lower redshift and the width represents the standard jackknife uncertainty.}         \label{fig:qf}
    \end{center}
\end{figure*}

@@

For our PRIMUS sample at $z \sim 0.3$, over $10^{9.5} \mathcal{M}_{\odot} < \mathcal{M}_{*} < 10^{11} \mathcal{M}_{\odot}$ $f_{\mathrm{Q}}$ ranges from $\sim 0.2$ to $\sim 0.65$ for low density environment, while at high density environment $f_{\mathrm{Q}}$ ranges from $\sim 0.2$ to $\sim 0.8$. Similarly, at $z \sim 0.5$, over $10^{10} \mathcal{M}_{\odot} < \mathcal{M}_{*} < 10^{11.2} \mathcal{M}_{\odot}$ $f_{\mathrm{Q}}$ ranges from $\sim 0.3$ to $\sim 0.6$ for low density environment and $f_{\mathrm{Q}}$ ranges from $\sim 0.3$ to $\sim 0.7$ for high density environments. Finally in our highest redshift bin $z \sim 0.7$, over the mass range $10^{10.5} \mathcal{M}_{\odot} < \mathcal{M}_{*} < 10^{11.5} \mathcal{M}_{\odot}$, $f_{\mathrm{Q}}$ ranges from $\sim 0.35$ to $\sim 0.6$ for low density and $\sim 0.45$ to $\sim 0.8$ for high density. For the entire redshift range of our sample, $f_{\mathrm{Q}}$ in high density environment is higher than $f_{\mathrm{Q}}$ in low density environments.

{\bf We note that for $\mathcal{M}_* < 10^{10} \mathcal{M}_{\odot}$ at $z \sim 0.3$, we find no significant difference between $f_\mathrm{Q}$ in low and high density environments. Similar quiescent/red fraction studies (e.g. \citealt{Baldry:2006aa, Cucciati:2010aa}) find, at these redshifts and mass range, a greater environment dependence in $f_\mathrm{Q}$. However we note that, at $\mathcal{M}_* < 10^{10} \mathcal{M}_{\odot}$ at $z \sim 0.3$, only three of the five PRIMUS fields used in our analysis (XMM-SXDS, XMM-CFHTLS, and COSMOS; see Section \ref{sec:primus}) contribute galaxies to our sample. As a result our jack-knife uncertainties, which are calculated by excluding one PRIMUS field at a time, underestimate the uncertainty from cosmic variance especially since the PRIMUS fields XMM-SXDS and XMM-CFHTLS are adjacent fields. A rough estimate of the cosmic variances using the expressions derived in \cite{Driver:2010aa} put cosmic variance uncertainties $> 60 \%$. This estimate does not take into account the unique geometry of the PRIMUS fields or the edge-cuts, which only increase the cosmic variance uncertainties. Therefore, the quiescent fraction comparison at $z \sim 0.3$ for $\mathcal{M}_{*} < 10^{10} \mathcal{M}_\odot$ cannot be accurately made from our PRIMUS sample.}

@@

\begin{figure}
    \begin{center}
        \leavevmode
        \epsscale{1.0}
        \epsfig{file=fig5.pdf, height=0.45\textwidth}
        \caption{The evolution of the quiescent fraction at fiducial
          mass, $f_{Q}(\mathcal{M}_{\mathrm{fid}})$, for low (blue) and
          high (red) density environments within the redshift range $z
          = 0.0 - 0.8$. We present the $f_{Q}(\mathcal{M}_{\mathrm{fid}})$
          evolution for $\mathcal{M}_{\mathrm{fid}} = 10^{10.5}
          \mathcal{M}_\odot$ (solid fill) and $10^{11}
          \mathcal{M}_\odot$ (patterned fill) with the uncertainty of
          the best-fit parameter $b$ in Equation \ref{eq:qffit}
          represented by the width of the line. While the high density $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$ is greater than low density environment $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$ over the entire redshift range of our sample, there is a significant increase in $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$ over cosmic time for both environments. {\bf For the environment cut-offs ($n_{\mathrm{env}} =0.0 $ for low }and $n_{\mathrm{env}} > 3.0$ for high), there is no significant difference in the slope of the evolution between the environments.}         \label{fig:qffit}
    \end{center}
\end{figure}
